An empirical study of fixation for strategies in the Iterated Prisoner's Dilemma

### 2017-04-28 tex/main.tex
Make possible to get p_1 when p_N/2 incomplete.

In this section \(x_i\) will be investigated: the probability of 1 individual of
a given type successfully becoming fixated in a population of \(N - 1\) other
individuals. Figures~\ref{fig:fixation_heatmap_invade} shows these values for
the players along the vertical axis when matched against the players on the
horizontal axis. It can be seen that invasion is in general more challenging for
\(N=7\) and \(N=11\) in comparison to \(N=3\).
%TODO Change this to N=14
This information is summarised in Figure~\ref{fig:fixation_boxplot_invade}
showing the median fixation as well as the neutral fixation for each given
scenario.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_3_invade.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_11_invade.pdf}
        \caption{\(N=11\)}

    %TODO Replace N=11 with N=14
    \end{subfigure}%

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_3_invade.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_11_invade.pdf}
        \caption{\(N=11\)}
    \end{subfigure}%

    % TODO Replace N=11 with N=14 (when we have more data).
    \caption{Median probabilities \(x_{1}\) of all strategies as well as the
    neutral fixation probability}
    \label{fig:fixation_boxplot_invade}
\end{figure}

For \(N\in\{3, 7, 11\}\) the top five strategies are given in
% TODO Change N=11 to N=14
Tables~\ref{tbl:top_five_invade}.

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_3_invade.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_7_invade.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_11_invade.tex}
        \caption{\(N=11\)}
    \end{subfigure}
    %TODO Change N=11 to N=14
    \caption{Properties of top five invaders}
    \label{tbl:top_five_invade}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_3_resist.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_11_resist.pdf}
        \caption{\(N=11\)}

    %TODO Replace N=11 with N=14
    \end{subfigure}%

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_3_resist.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_11_resist.pdf}
        \caption{\(N=11\)}
    \end{subfigure}%

    % TODO Replace N=11 with N=14 (when we have more data).
    \caption{Median probabilities \(x_{N-1}\) of all strategies as well as the
    neutral fixation probability}
    \label{fig:fixation_boxplot_resist}
\end{figure}

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_3_resist.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_7_resist.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_11_resist.tex}
        \caption{\(N=11\)}
    \end{subfigure}
    %TODO Change N=11 to N=14
    \caption{Properties of top five strategies resistors}
    \label{tbl:top_five_invade}
\end{table}

@@

    \begin{subfigure}{\textwidth}
        \centering
        \input{"../tbl/correlation_coeficients_coexist.tex"}
        \caption{Correlation coefficients for ranks for coexistance}
        \label{tbl:correlation_coeficients_coexist}
    \end{subfigure}
    \caption{Correlation coefficients}
\end{table}

\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_invade.pdf}
		\caption{Rank based on \(x_1\)}
    \end{subfigure}
    ~
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_resist.pdf}
        \caption{Rank based on \(x_{N - 1}\)}
    \end{subfigure}
    ~
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_coexist.pdf}
        \caption{Rank based on \(x_{N/2}\)}
    \end{subfigure}
    \caption{Correlation coefficients for ranks}
    \label{fig:correlation_coefficients}
\end{figure}

>>>>

In this section \(x_i\) will be investigated: the probability of 1 individual of
a given type successfully becoming fixated in a population of \(N - 1\) other
individuals. Figures~\ref{fig:fixation_heatmap_invade} shows these values for
the players along the vertical axis when matched against the players on the
horizontal axis. It can be seen that invasion is in general more challenging for
\(N=7\) and \(N=12\) in comparison to \(N=3\).
%TODO Change this to N=14
This information is summarised in Figure~\ref{fig:fixation_boxplot_invade}
showing the median fixation as well as the neutral fixation for each given
scenario.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_3_invade.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_invade.pdf}
        \caption{\(N=12\)}

    %TODO Replace N=12 with N=14
    \end{subfigure}%

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_3_invade.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_12_invade.pdf}
        \caption{\(N=12\)}
    \end{subfigure}%

    % TODO Replace N=12 with N=14 (when we have more data).
    \caption{Median probabilities \(x_{1}\) of all strategies as well as the
    neutral fixation probability}
    \label{fig:fixation_boxplot_invade}
\end{figure}

For \(N\in\{3, 7, 12\}\) the top five strategies are given in
% TODO Change N=12 to N=14
Tables~\ref{tbl:top_five_invade}.

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_3_invade.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_7_invade.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_12_invade.tex}
        \caption{\(N=12\)}
    \end{subfigure}
    %TODO Change N=12 to N=14
    \caption{Properties of top five invaders}
    \label{tbl:top_five_invade}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_3_resist.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_resist.pdf}
        \caption{\(N=12\)}

    %TODO Replace N=12 with N=14
    \end{subfigure}%

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_3_resist.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_12_resist.pdf}
        \caption{\(N=12\)}
    \end{subfigure}%

    % TODO Replace N=12 with N=14 (when we have more data).
    \caption{Median probabilities \(x_{N-1}\) of all strategies as well as the
    neutral fixation probability}
    \label{fig:fixation_boxplot_resist}
\end{figure}

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_3_resist.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_7_resist.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_12_resist.tex}
        \caption{\(N=12\)}
    \end{subfigure}
    %TODO Change N=12 to N=14
    \caption{Properties of top five strategies resistors}
    \label{tbl:top_five_invade}
\end{table}

@@

    \begin{subfigure}{\textwidth}
        \centering
        \input{"../tbl/correlation_coeficients_coexist.tex"}
        \caption{Correlation coefficients for ranks for coexistance}
        \label{tbl:correlation_coeficients_coexist}
    \end{subfigure}
    \caption{Correlation coefficients of rankings by population size}
\end{table}

\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_invade.pdf}
		\caption{Rank based on \(x_1\)}
    \end{subfigure}
    ~
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_resist.pdf}
        \caption{Rank based on \(x_{N - 1}\)}
    \end{subfigure}
    ~
	\begin{subfigure}[t]{.3\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_coexist.pdf}
        \caption{Rank based on \(x_{N/2}\)}
    \end{subfigure}
    \caption{Heatmap of correlation coefficients of rankings by population size}
    \label{fig:correlation_coefficients}
\end{figure}
